---
title: "Rubem Dornas's resume"
author: Rubem Dornas
date: "`Sys.Date()`"
output:
  pagedown::html_resume:
    css: 
      - override.css         # OVERIDE CERTAIN FUNCTIONS OF CSS
      - resume               # DEFAULT FILE
    # set it to true for a self-contained HTML page but it'll take longer to render
    self_contained: true
# uncomment this line to produce HTML and PDF in RStudio:
knit: pagedown::chrome_print
---
```{r include=FALSE}
Sys.setlocale("LC_TIME", "C")

hoje_ordinal <- scales::ordinal(lubridate::day(Sys.Date()))

hoje <- lubridate::day(Sys.Date())

mes <- lubridate::month(Sys.Date(), label = TRUE, abbr = TRUE)

ano <- lubridate::year(Sys.Date())

data_completa <- sprintf("%s %s, %s", mes, hoje, ano)
```

# Aside

![Rubem Dornas](https://avatars.githubusercontent.com/u/25906665?v=4){width="80%"}

## Contact Info {#contact}

- <i class="fa fa-envelope"></i> [rapdornas\@gmail.com](mailto:rapdornas@gmail.com){.email}
- <i class="fa fa-github"></i> [github.com/rdornas](https://github.com/rdornas)
- <i class="fa fa-phone"></i> +1 (352) 709-0128
- For more information, please contact me via email.

## Skills {#skills}

• Experienced in field biology and ecology, specially concerning wildlife and road/railroad ecology.

• Highly skilled in R, develops web apps in Ruby on Rails.

• Experienced with geoprocessing programming in R.

• Acting in IT projects since 2019.

## Disclaimer {#disclaimer}

Last updated on `r data_completa`.<br>
Updated CV at [rdornas.github.io/CV](https://rdornas.github.io/CV)

# Main

## Rubem Dornas {#title}

### Biologist turned IT professional

I hold a B.Sc. in Biological Sciences from Universidade Federal de Minas Gerais (UFMG), Brazil, along with a specialization in Geoprocessing from Pontifícia Universidade Católica de Minas Gerais (PUC-MG) and an M.Sc. in Analysis and Modeling of Environmental Systems from UFMG. With over ten years of experience in environmental consulting for leading regional and global firms, I developed strong skills in data analysis and technical writing. I have also authored and peer-reviewed scientific publications on environmental topics. More recently, I have transitioned into the IT domain, where I operate at the intersection of data, technology, and product development. I contribute to data analysis workflows, support development teams, and act as a Product Owner, bringing a versatile, cross-functional profile that bridges technical and business perspectives.

## Education {data-icon="graduation-cap" data-concise="true"}

### Universidade Federal de Minas Gerais

Lic. in Biological Sciences

Belo Horizonte, Brazil

2003 - 2007

Thesis: Peculiarities, curiosities and myths of birds as a tool for basic teaching of Ornithology (in Portuguese)

### Universidade Federal de Minas Gerais

BSc. in Biological Sciences - Vertebrates' Zoology

Belo Horizonte, Brazil

2008 - 2010

Thesis: Study of wild vertebrates road-kills on Serra do Rola-Moça State Park, Minas Gerais (in Portuguese)

### Pontifícia Universidade Católica de Minas Gerais

Specialization in Geoprocessing

Belo Horizonte, Brazil

2016 - 2018

Thesis: Geoprocessing applied to the environment area: a case study based on quantitative methods of spatial analysis (in Portuguese)

### Universidade Federal de Minas Gerais

MSc. in Analysis and Modeling of Environmental Systems

Belo Horizonte, Brazil

2017 - 2019

Thesis: Estimations and temporal and spatial patterns of fatalities of cane toads (_Rhinella_ gr. _marina_) on Brazilian Amazonian railroad (in Portuguese)

## Professional Experience (last 3) {data-icon="suitcase"}

### Biologist / Project Coordinator

AECOM

Belo Horizonte, Brazil

Current - 2020

::: concise
-   Involved in auditing of minings tailings dams.
-   Development of reports and presentations.
-   Creation, development (including code) and maintenance of a new technological platform for controlling audits recommendations.
-   Product Owner (IT position) of a new digital tool for the company.
:::

### Data Scientist

Amplo Engenharia e Gestão de Projetos

Belo Horizonte, Brazil

2020

::: concise
-   Planning and elaboration of digital forms for field data collection
-   Planning and elaboration of computational scripts and packages in R programming for extracting and including information in relational databases
-   Data analysis and report writing
:::

### Biologist

Amplo Engenharia e Gestão de Projetos

Belo Horizonte, Brazil

2017 - 2011

::: concise
- Member of the technical and coordination teams concerning several environmental studies related to mining and transportation.
- Responsible for the fauna studies needed to the expansion of Estrada de Ferro Carajás (EFC), under concession by Vale S.A.
- Responsible for presentations on behalf of the company to different audiences
:::


## Selected Publications {data-icon="file"}

### Camera trap surveys of Atlantic Forest mammals: A data set for analyses considering imperfect detection (2004-2020)

Ecology. v. 105, p. e4298. [![DOI](https://raw.githubusercontent.com/jpswalsh/academicons/master/svg/doi.svg){width="3.5%"}](https://dx.doi.org/10.1002/ecy.4298)

N/A

2024

Franceschi IC, **Dornas RAP**, Lermen IS, et al.

### The need to consider searcher efficiency and carcass persistence in railway wildlife fatality studies

Eur. J. Wildl. Res. 66:81. [![DOI](https://raw.githubusercontent.com/jpswalsh/academicons/master/svg/doi.svg){width="3.5%"}](https://doi.org/10.1007/s10344-020-01417-7)

N/A

2020

Dasoler BT, Kindel A, Beduschi J, Biasotto LD, **Dornas RAP**, Gonçalves LO, Lombardi PM, Menger T, de Oliveira GS & Teixeira FZ.

### Strain by the train: Patterns of toad fatalities on a Brazilian Amazonian railroad

Sci. Total Environ., 660:493-500. [![DOI](https://raw.githubusercontent.com/jpswalsh/academicons/master/svg/doi.svg){width="3.5%"}](http://dx.doi.org/10.1016/j.scitotenv.2018.12.371)

N/A

2019

**Dornas RAP**, Teixeira FZ, Gonsioroski G & Nóbrega RAN.

### On a collision course: the vulnerability of bats to roadkills in Brazil

Mastozool. Neotrop. 25(1):115-128. [![DOI](https://raw.githubusercontent.com/jpswalsh/academicons/master/svg/doi.svg){width="3.5%"}](http://ref.scielo.org/555mqy)

N/A

2018

Novaes RLM, Laurindo RS, **Dornas RAP**, Esbérard CAL & Bueno C.

### Record of the Giant Otter, _Pteronura brasiliensis_ (Zimmermann, 1780), (Carnivora: Mustelidae) in a fragmented landscape of Maranhão state, Brazil

Checklist 13(1):2041. [![DOI](https://raw.githubusercontent.com/jpswalsh/academicons/master/svg/doi.svg){width="3.5%"}](https://doi.org/10.15560/13.1.2041)

N/A

2017

Prist PR, **Dornas RAP**, dos Santos RH, Torres LGC & Lima ELP.

## Other relevant information {data-icon="lightbulb"}

::: concise
- Reviewer for several academic journals.
- Multiple concluded works for environmental companies as a senior consultant.
- Active member of NERF / UFRGS - Núcleo de Ecologia de Rodovias e Ferrovias / Universidade Federal do Rio Grande do Sul.
- French proficiency: Diplôme Approfondi de Langue Française / DALF (2003).
:::

```{r include=FALSE}
pdf_files <- list.files(
  path = ".",
  pattern = "\\.pdf$",
  full.names = TRUE,
  recursive = FALSE,
  ignore.case = TRUE
)

if (length(pdf_files) > 0) {
  file.remove(pdf_files)
}

today <- lubridate::today() |> stringr::str_remove_all("-")

output_file <- glue::glue("cv_rdornas_{today}.pdf")

pagedown::chrome_print(
  "index.html",
  output = output_file,
  browser = "/Applications/Comet.app/Contents/MacOS/Comet"
)
```
